\documentclass{article}
\usepackage[utf8]{inputenc}

\title{PS1}
\author{Alex Skipper }
\date{January 2018}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Introduction}
My interest in Economics started in High School, taking an AP Econ class. It was not until I was at a junior college, trying to figure out what I want to do, that I really got in Economics and how everyday life can be applied to it. Noticing what I learned in class and being able to apply and see my knowledge to everyday situations really increased my interest in economics. What made me want to take this class, was the possibility of learning new programs and machine learning. Additionally, many of the students that are enrolled, I have had multiple classes with, so most of us decided to take the class together. Plus, Dr. Wang recommended this class. As for the project; I have a few ideas, such using my research project about the Energy Efficient Residential Construction Tax Credit for Oklahoma. Only if the data and Dr. Rogers will allow it.  I am also thinking about doing something with education, sports, or any other possible idea that I come across. My goal for the class is to do well, but also to get a starting point for  computer programs so I can continue my learning after school. My plan after graduation is still up in the air. I have four broad options: work in Forth Worth, TX with or without my dad, work in Oklahoma, on the East or West coast, or just work out of the country. As for where out of the country, anywhere where I can get a job. I am excited to take this class and learn a lot.



\section{Equations}
\centering
$$\{a^2+b^2=c^2\}$$
\end{document}}

